Scaffolder - Software for Microbial Genome Scaffolding.

### 2011-03-01 src/article.tex
Add reason for scaffolder at top of discussion

The aims of Scaffolder are twofold. The first is providing software that is
easy to install and simplifies the task of genome finishing. The second aim is
to facilitate reproducibility when joining large nucleotide sequences together
to create a genome sequence. \pb

>>>>

Scaffolding is a intermediate stage in a genome project. Additional sequences
are produced using a combination of computational and laboratory methods. These
new sequences are then added to existing sequencing data to produce
a continuous sequence of the target organism genome. The scaffolding process
however is a laborious manual process involving joining and adding large
regions of nucleotide sequence together. Any manual process is inherently hard
to reproduce and introduces the possibility of human error. The aims of
Scaffolder are therefore twofold. The first is providing software that is easy
to install and simplifies the task of genome finishing. The second aim is to
facilitate reproducibility when joining large nucleotide sequences together to
create a genome sequence. \pb
